### 2016-01-05 p2/rec-intro.tex
Style updates

If we start with two copies of the filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A:=A\aFS$
and $\FS_B:=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
so that $\recb\aFS_A$ and $\reca\aFS_B$ would be as close to each other as possible.

>>>>

If we start with two copies of the filesystem $\FS$,
and two different sequences are applied to the copies to yield $\FS_A=A\aFS$
and $\FS_B=B\aFS$, then our aim is to define sequences of commands $\reca$ and $\recb$
so that $\recb\aFS_A$ and $\reca\aFS_B$ would be as close to each other as possible.
